Lightness constancy under fixed geometry

### 2017-12-14 Draft1/draft1.tex
added references

\section{Introduction}
The color of an object has important behavioral implications. This important property of an object is perceived from the light reflected off its surface. The reflected light depends not just on the properties intrinsic to the object, such as the object's surface reflectance, its texture, material properties and geometry (shape, size, orientation), but also on extrinsic factors that depend on the object's surround (Fig. \ref{fig:introSchematic}). These extrinsic factors, such as the surface reflectance, texture and material properties of the objects in the surround, the illumination spectrum of the sources of light illuminating the object, the geometry, relative position and pose of the objects and light sources in the surround, and the position of the observer, vary considerably from scene to scene. The challenge faced by the visual system is to recover a stable perceptual representation of the object's surface reflectance invariant of the extrinsic factors. The ability of the visual system to extract such a stable representation, its perceived color, is called color constancy. We are interested in identifying the computations that lead to such constancy.

@@

% Figure 1: Introduction
\begin{figure}
\centering
\begin{subfigure}{0.4 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_a.png}
        \caption{}
        \label{fig:introSchematic}
    \end{subfigure}
    \begin{subfigure}{0.45 \textwidth}   
        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_b.jpeg}
        \caption{}
        \label{fig:introExampleFigure}
    \end{subfigure}
    \label{introFigure}
    \caption{(a) {\bf Color Constancy:} The light coming from an object to our eyes depends both on the surface reflectance of the object, $R(\lambda,x)$, and the illumination spectrum of the light source, $E(\lambda,x)$. Additionally, it depends on the context in which the object lies. The human visual system has the ability to discard any variations in the captured light due to extrinsic factors, and stably perceive the color of the object. Such invariant color perception is called color constancy. (b) {\bf Lightness Constancy Under Spectral Variations:} In this work we study lightness estimation. Fig.\ref{fig:introExampleFigure} shows images of an object (spherical object in the center) at three lightness levels. We show 5 images at each lightness level which vary in the spectra of the target object (sphere), the background objects and the light sources. (For illustration, in fig.\ref{fig:introExampleFigure}, we have fixed the shape of the target object reflectance spectra along the column.) Our aim is to identify computations that can accurately estimate the object lightness under such variations.} 
\end{figure}

>>>>

\section{Introduction}
The perceived color of an object has important behavioral implications, since color helps us to identify objects and their properties \cite{Mollon89, Jacobs81}.
Perceived object color is not sensed directly, rather it is computed by the brain starting with the retinal image of light reflected from the object to the eye.
The challenge of object color perception is that this reflected light depends not just on the object's surface reflectance, but also on extrinsic factors such as the illumination, the object's pose,
and the position of the observer (Fig. \ref{fig:introSchematic}).
Thus, to produce a stable perceptual representation of an object's surface reflectance in the face of variation in these extrinsic factors, the brain must account for their influence on the reflected light.
The ability of a visual system to extract such a stable representation is called color constancy. Although human color constancy is by no means perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}. 
In this paper, we consider the computational problem of color constancy, that is how in principle could a visual system process the light reflected to the eyes to produce percepts well-correlated with object surface reflectance.

% Figure 1: Introduction
\begin{figure}
\centering
\begin{subfigure}{0.4 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_a.png}
        \caption{}
        \label{fig:introSchematic}
    \end{subfigure}
    \begin{subfigure}{0.45 \textwidth}   
        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_b.jpeg}
        \caption{}
        \label{fig:introExampleFigure}
    \end{subfigure}
    \label{introFigure}
    \caption{(a) {\bf Color Constancy:} The light reflected from an object to our eyes depends both on the surface reflectance of the object, $R(\lambda,\vec{x})$, and the illumination spectrum of the light source, $E(\lambda,\vec{x})$. Additionally, it depends on geometric factors, such as the object's shape and pose as well as the position of the observer. The human visual system is able to account for, at least partially, variations in the reflected light due to such extrinsic factors, and produce a percept of object color that is relatively stable with respect to such variations. Such invariant color perception is called color constancy. (b) {\bf Lightness Constancy Under Spectral Variations:} In this paper we consider the special case of lightness constancy. Fig.~\ref{fig:introExampleFigure} shows images of an object (the sphere in the center of each image) at three levels of object luminance. Within each row, the surface reflectance of the spheres has the same luminance, when illuminated by a standard reference illuminant, CIE D65. The three rows differ in this value, as can be seen by the fact that the lightness of the spheres generally decreases as we move down the rows. Within each row, the relative surface reflectance of the spheres varies, as can be seen by the variation in color appearance across the each row.  Within each column, this relative surface reflectance is held fixed. In this paper, we seek to identify computations that accurately estimate object luminance across variations in relative surface reflectance, variations in illumination, and variation in the reflectance of other objects in the scene.}
 \end{figure}

There is a considerable literature on computational color constancy. Seminal work considered a reduced scene model in which flat matte surfaces were illuminated by a single spatially diffuse illuminant and explored algorithms that could either recover a descriptor correlated with object surface reflectance (e.g. \cite{LandRetinex}) or explicit estimates of object surface reflectance and/or illuminant spectral power distribution (e.g., \cite{LandRetinex,Buchsbaum80,MaloneyWandell86}.
An important insight of this line of research was that to account for variation in illumination, it was necessary to consider the light reflected from the entire scene. That is, although good constancy cannot be achieved in the face of illuminant variation if one considers only the light reflected from a single target object, when one considers the entire image it is possible to use the joint variation in light reflected from many objects to obtain (either implicitly or explicitly) an estimate of the illuminant common across the objects, and in turn to use this estimate to produce a stabilized representation of object color.
At the same time, this processing introduces an additional dependence.  Although the reflectance of the objects surrounding an object of interest has little direct effect on the light reflected from the object of interest, variation in the reflectance of the surrounding objects can have a large effect on the output of constancy algorithms that process the entire image \cite{BrainardWandellRetinex}.
Thus, a key aspect evaluating computational constancy algorithms is not only to ask about target object color stability with respect to variation in illumination, but also to ask about target object color stability with respect to the surface reflectance of other objects in the scene.
Subsequent computational constancy work sought to generalize both the image formation model to include richer geometric descriptions and to incorporate probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}; LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS).

% NEED TO MOTIVATE WHAT WE'RE GOING TO DO.  SUPERVISED LEARNING APPROACH USING VIRTUAL WORLD DATA TO GET LABELLED TRAINING DATA.

% IN THIS PAPER, WILL APPLY OUR APPROACH TO A REDUCED VERSION OF THE PROBLEM, AS A FIRST STEP

@@
